---
title: "Matrix Operations"
author: "Nir Ben Laufer"
date: '2023-05-16'
output: html_document
---


(X\^t \* X)\^-1

-   QR Decomposition

    A (nxp) = Q (nxn) \* R (nxp)

    A\^-1 = (QR)\^-1

    A \~ Q1R1 where Q1, R1 getting rid of redudant dimensions b/c the first couple terms are the most significant (STAT419)

    A \~ (Q1R1)\^-1

    (Q1R1)\^-1 \* A \~ I (identiy matrix)

    B = (X\^t \* X)\^-1 \* X\^T \* Y (X\^t \* X)\^-1 -\> QR - \> Q1R1

    B \~ (Q1R1)\^-1 \* X\^T \* Y

-   Goal

    LSE (least square estimate) -\> min sum(i=1 to n) (yi \* yi\^)2

    Want Beta where derivative = 0 of Sq Error function to find min (Only doign one beta at a time)

    derivative sum(i=1 to n) (yi \* yi\^)2 -\> sum(i=1 to n) 2 (yi 9 Bxi\^) \* -xi

    -   Steps

        1)  Choose starting B -\> Start at B=0 -\> Can you be more clever?

        2)  Find slope at B -\> negative slope = increase -\> positive slope = decrease -\> slope \~ 0 = stop got right data This means finding the derivative at ever Beta val

        3)  Update Slope -\> new B = old B - slope\*(eta) -\> Where you choose eta

        4)  Repeat -\> until you hit stopping condition

    -   Ways the steps could turn out

    -   Slowly make it to the stopping point (0)

    -   Keep overshooting a little at a time till you get to 0

    -   Keep overshooting by too much until you never get to 0

-   For this week write a function that keeps interating till you get to 0

    -   Advice

        1)  Build in a "failsafe" -\> Stop after \# of interactions -\> stop after time passes
        2)  Build "checks" as you go -\> B1=1 -\> B2=-10 ...
        3)  Get clever about initial B or about Eta MAE = sum \| yi - yi\^ \|

        Standardize all your predictors X and update unit test set.seed()
        
```{r, echo = FALSE}


print("no code shown in knit (echo = FALSE)")


```

```{r, warning = FALSE}

# Define a custom function
math_function <- function(x) {
  if (x < 0) {
    warning("Input value should be non-negative!")
  }
  return(x^2)
}

# Call the function with a negative input
result <- math_function(-5)

# Output the result
print("entered result <- math_function(-5) which should give error, but used warning = FALSE in R chunk")
print(result)

```