---
title: "Stat 431 Final Portfolio"
format: pdf
editor: visual
self-contained: true
toc: true
---

```{r, include = FALSE}
library(tidyverse)
portfolio_levels <- tibble()
names(portfolio_levels) <- c("Objective", "Level")
```

# Independent Learning (IL):

*These objectives show your ability to seek out new information and adapt to new tools to solve data analysis problems.*

------------------------------------------------------------------------

## \[IL-1\] Adding new skills:

-   I can find and adopt new packages to accomplish tasks.
-   I can adapt to different syntax styles (tidy, base, formula style, data.table).
-   I can use tutorials, etc. to enhance my understanding of new concepts

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 5

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "IL-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can find and adopt new packages to accomplish tasks.
    -   incorporated boot package:

        -   https://github.com/josh-rowe/lab-1-review/commit/4d650cda5c7ff8f5d98b69557caff2ba26d80571
-   I can adapt to different syntax styles (tidy, base, formula style, data.table).
    -   used Base:

        -   https://github.com/josh-rowe/lab-1-review/commit/ddb00f1e729ecbfa1d711a0481c841f00ce055f7?diff=unified

    -   used tidy:

        -   https://github.com/BLauf/lab-2-visualization-fork-BLauf/commit/ebc897fb170f61fbdd8c1ad5ba246955b86cbdaf
-   I can use tutorials, etc. to enhance my understanding of new concepts
    -   used boot package tutorial to incorporate package

        -   https://cran.r-project.org/web/packages/bootstrap/bootstrap.pdf

------------------------------------------------------------------------

## \[IL-2\] Online resources:

-   I can use online resources (Google, ChatGPT, StackOverflow) to solve problems, debug, or find new tools.
-   I can find source code for similar projects to use as starting points for my own
-   I can read the documentation of an API to figure out how to access data.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 5

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "IL-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can use online resources (Google, ChatGPT, StackOverflow) to solve problems, debug, or find new tools.
    -   Refrenced StackOverflow as well as Chat GPT several times

        -   https://github.com/josh-rowe/lab-1-review/commit/4d650cda5c7ff8f5d98b69557caff2ba26d80571

        -   https://github.com/BLauf/lab-2-visualization-fork-BLauf/commit/ebc897fb170f61fbdd8c1ad5ba246955b86cbdaf
-   I can find source code for similar projects to use as starting points for my own
    -   https://github.com/josh-rowe/lab-1-review/commit/4d650cda5c7ff8f5d98b69557caff2ba26d80571
-   I can read the documentation of an API to figure out how to access data.
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/5d039fe53e72fafc37f61bb4fc2f14215920c9b6

------------------------------------------------------------------------

# Reproducible Workflow (RW):

*These objectives show your ability to produce artifacts and deliverables that are organized, documented, version tracked, and responsibly designed.* \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

## \[RW-1\] File, code, and data management:

-   I can use Git and GitHub to track my progress and collaborate (creating repos, cloning, forking, pull requesting).
-   I always use R Projects and the {here} package to organize my scripts, notebooks, data, and applications.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "RW-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can use Git and GitHub to track my progress and collaborate (creating repos, cloning, forking, pull requesting).
    -   https://github.com/Blauf-Practice/BLauf-GitHub_Justification/commit/ff53b94d0f3601cf6aa10bb6d33870c7324baa15
-   I always use R Projects and the {here} package to organize my scripts, notebooks, data, and applications.
    -   read in data to github:

        -   https://github.com/BLauf/lab-2-visualization-fork-BLauf/commit/c401544a0da36b9fd12954b2606d9dfcca4c7a1c

    -   read in data to R using {here} package

        -   https://github.com/BLauf/lab-2-visualization-fork-BLauf/commit/d283d6ea4c6b4324510109039ef48db5f2a5dec5

------------------------------------------------------------------------

## \[RW-2\] Notebooks:

-   I can use Quarto and/or R Markdown to produce a reproducible notebook and polished rendered document.
-   I can use appropriate chunk options (echo, error, cache, etc.) to render my qmd/Rmd quickly and cleanly.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "RW-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can use Quarto and/or R Markdown to produce a reproducible notebook and polished rendered document.
    -   https://github.com/Blauf-Practice/BLauf-GitHub_Justification/commit/ff53b94d0f3601cf6aa10bb6d33870c7324baa15
-   I can use appropriate chunk options (echo, error, cache, etc.) to render my qmd/Rmd quickly and cleanly.
    -   https://github.com/Blauf-Practice/BLauf-GitHub_Justification/commit/ff53b94d0f3601cf6aa10bb6d33870c7324baa15

------------------------------------------------------------------------

## \[RW-3\] Code style

-   My code is clear, readable, well-organized, and well-commented.
-   I can use a package-based workflow to organize my analyses

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "RW-3", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   My code is clear, readable, well-organized, and well-commented
    -   https://github.com/shreyaaar/VectorVerse/commit/36eaf95d5cddc9cd8513daf01720dc1e2e03cc69
-   I can use a package-based workflow to organize my analyses
    -   https://github.com/shreyaaar/VectorVerse/commit/36eaf95d5cddc9cd8513daf01720dc1e2e03cc69

------------------------------------------------------------------------

# Technical Communication (TC):

*These objectives show your ability to communicate the processes you have implemented in your code, as well as the data conclusions and results.*

------------------------------------------------------------------------

## \[TC-1\] Project summaries:

-   I can clearly and succinctly summarize the contributions of my project.
-   I accurately interpret statistical or modeling results.
-   I consider the appropriate scope and impact of my project results.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 3

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "TC-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can clearly and succinctly summarize the contributions of my project.
    -   https://github.com/BLauf/Project-1-Interactive-Data-Exploration-Master/commits/main?after=289be1e2043ed9effee5edb9c92e17aa3ed5b345+34&branch=main&qualified_name=refs%2Fheads%2Fmain
-   I accurately interpret statistical or modeling results.
-   I consider the appropriate scope and impact of my project results.

------------------------------------------------------------------------

## \[TC-2\] Documentation:

-   I provide ample documentation and tutorials for my custom functions.
-   I provide user-friendly guides for my tools and sofware

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "TC-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I provide ample documentation and tutorials for my custom functions.
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/d638433c1beba2372c22a60579aabd1599dcb0fc
-   I provide user-friendly guides for my tools and sofware
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/d638433c1beba2372c22a60579aabd1599dcb0fc

------------------------------------------------------------------------

# Data Manipulation (DM):

*These objectives relate to the collection, cleaning, processing, and preparing of datasets for analysis.*

------------------------------------------------------------------------

## \[DM-1\] Data preparation:

-   I can read in datasets to R, including untidy ones.
-   I can clean datasets to deal with missing data, typos, poor formatting, etc.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "DM-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can read in datasets to R, including untidy ones. Maybe?
    -   https://github.com/Cal-Poly-Advanced-R/lab-2-visualization-BLauf/commit/ebc897fb170f61fbdd8c1ad5ba246955b86cbdaf
-   I can clean datasets to deal with missing data, typos, poor formatting, etc.
    -   https://github.com/Cal-Poly-Advanced-R/lab-2-visualization-BLauf/commit/ebc897fb170f61fbdd8c1ad5ba246955b86cbdaf

------------------------------------------------------------------------

## \[DM-2\] Data wrangling

-   I can cleverly use pivoting, grouping, and joining to wrangle data.
-   I can use mapping ({purrr}), applying (tapply, lapply, ...), and/or iteration (for loops) to perform repeated tasks.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "DM-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can cleverly use pivoting, grouping, and joining to wrangle data.
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/5d039fe53e72fafc37f61bb4fc2f14215920c9b6
-   I can use mapping ({purrr}), applying (tapply, lapply, ...), and/or iteration (for loops) to perform repeated tasks.
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/5d039fe53e72fafc37f61bb4fc2f14215920c9b6

------------------------------------------------------------------------

## \[DM-3\] Data collection

-   I can use API urls to access JSON data and convert it to a data frame
-   I can webscrape simple tables and information

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 3

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "DM-3", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can use API urls to access JSON data and convert it to a data frame
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/5d039fe53e72fafc37f61bb4fc2f14215920c9b6
-   I can webscrape simple tables and information
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/5d039fe53e72fafc37f61bb4fc2f14215920c9b6

------------------------------------------------------------------------

# Professional Visualization (PV):

------------------------------------------------------------------------

## \[PV-1\] ggplot: grammar of graphics

-   I can use less common geometries, including those from ggplot extension packages.
-   I can use the correct aesthetics to map variables
-   I understand how geometries inherit aesthetics I can add annotations to my plot

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "PV-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can use less common geometries, including those from ggplot extension packages.
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/085a00999235dd2bdbdad617674b076330686f12
-   I can use the correct aesthetics to map variables
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/085a00999235dd2bdbdad617674b076330686f12
-   I understand how geometries inherit aesthetics I can add annotations to my plot
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/085a00999235dd2bdbdad617674b076330686f12

------------------------------------------------------------------------

## \[PV-2\] ggplot: theme

-   I can edit the titles, subtitles, captions, axis labels, etc. to create a clearly labelled plot
-   I can choose colors ("scales") and themes to make a visually pleasing and accessible plot

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "PV-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can edit the titles, subtitles, captions, axis labels, etc. to create a clearly labelled plot
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/085a00999235dd2bdbdad617674b076330686f12
-   I can choose colors ("scales") and themes to make a visually pleasing and accessible plot
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/085a00999235dd2bdbdad617674b076330686f12

------------------------------------------------------------------------

## \[PV-3\] Dynamic visualizations

-   I can use a package like {gganimate} to create self-contained gifs
-   I can use a package like {plotly}, {ggplotly}, {leaflet}, {ggirafe}, etc. to make interactable html widgets

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "PV-3", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can use a package like {gganimate} to create self-contained gifs
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/ed99846086dbfb8b563e46ec58a64bd8629764b7
-   I can use a package like {plotly}, {ggplotly}, {leaflet}, {ggirafe}, etc. to make interactable html widgets
    -   used plotly:

        -   https://github.com/BLauf/lab-2-visualization-fork-BLauf/commit/ebc897fb170f61fbdd8c1ad5ba246955b86cbdaf

------------------------------------------------------------------------

## \[PV-4\] Shiny

-   I can create a functional Shiny app.
-   I understand the principle of reactivity, and how to use it.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 5

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "PV-4", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can create a functional Shiny app.
    -   https://github.com/BLauf/Project-1-Interactive-Data-Exploration-Master/commit/dcd7616d94a7ef050dc34960e0b8606523cede19
-   I understand the principle of reactivity, and how to use it.
    -   https://github.com/BLauf/Project-1-Interactive-Data-Exploration-Master/commit/dcd7616d94a7ef050dc34960e0b8606523cede19

------------------------------------------------------------------------

# Software Development (SD):

*These objectives relate to your ability to develop correct, usable, well-designed, and sophisticated software in the R language.*

------------------------------------------------------------------------

## \[SD-1\] R programming language details

-   I understand non-standard evaluation (aka "Tidy Eval" or "unquoted objects"), and I can use tunneling in my functions.
-   I understand functional programming, and I can use functions as objects in my code design
-   I understand object-oriented programming, and I can define my own classes and methods.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "SD-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I understand non-standard evaluation (aka "Tidy Eval" or "unquoted objects"), and I can use tunneling in my functions.
-   I understand functional programming, and I can use functions as objects in my code design
-   I understand object-oriented programming, and I can define my own classes and methods.

------------------------------------------------------------------------

## \[SD-2\] Package creation:

-   I can create a folder that is installable as an R package, possibly using {usethis} helper functions
-   I can document my functions using {roxygen2} style commenting
-   I can write and run unit tests using {testthat}
-   I can design a package that is user-friendly and has well-designed functions.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 4

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "SD-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can create a folder that is installable as an R package, possibly using {usethis} helper functions
    -   https://github.com/BLauf/STAT431-project-2-master/commit/9e201b1643ced6689d79f0d13ed51f43acd25864
-   I can document my functions using {roxygen2} style commenting
    -   https://github.com/BLauf/STAT431-project-2-master/commit/9e201b1643ced6689d79f0d13ed51f43acd25864
-   I can write and run unit tests using {testthat}
    -   https://github.com/BLauf/STAT431-project-2-master/commit/688c30a31ca2f7b599f9bf3b47c121692846b3fb
-   I can design a package that is user-friendly and has well-designed functions.
    -   https://github.com/BLauf/STAT431-project-2-master/commit/875f895cd369c7de4e3a56cd203a0fd03d4f66af

------------------------------------------------------------------------

# Matrix Operations (MO):

*These objectives show your ability to manipulate data-related information in the form of vectors and matrices, rather than in high-level data structures.*

------------------------------------------------------------------------

## \[MO-1\] Theory:

-   I understand the difference between ordinary multiplication and matrix multiplication, and how to implement each in R
-   I can implement and briefly explain the matrix equations for multiple linear regression and ridge regression

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "MO-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I understand the difference between ordinary multiplication and matrix multiplication, and how to implement each in R
    -   
-   I can implement and briefly explain the matrix equations for multiple linear regression and ridge regression
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/967e906931fcd5372d0c2837374335aa7fbfa549

------------------------------------------------------------------------

## \[MO-2\] Object structures:

-   I can convert data objects into the necessary matrix structures to perform operations on them.
-   I can convert results of matrix operations to convenient data analysis formats

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "MO-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can convert data objects into the necessary matrix structures to perform operations on them.
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/94edce81ecff974c15b15a8e25cad8ec9c7ad095
-   I can convert results of matrix operations to convenient data analysis formats
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/94edce81ecff974c15b15a8e25cad8ec9c7ad095

------------------------------------------------------------------------

# Algorithms and Iteration (AI):

*These objectives ask you to design code-based approaches to statistical computing problems, usually involving iteration to a stopping condition.*

------------------------------------------------------------------------

## \[AI-1\] Iteration to approximate value:

-   I can write a loop that updates values until a certain approximate stopping condition.
-   I can explain and implement gradient descent in simple cases.
-   I can choose reasonable starting conditions and step sizes.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "AI-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can write a loop that updates values until a certain approximate stopping condition.
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/94edce81ecff974c15b15a8e25cad8ec9c7ad095
-   I can explain and implement gradient descent in simple cases.
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/94edce81ecff974c15b15a8e25cad8ec9c7ad095
-   I can choose reasonable starting conditions and step sizes.
    -   

------------------------------------------------------------------------

## \[AI-2\] Iteration to exact convergence:

-   I can write a loop that updates values until perfect convergence is reached.
-   I can explain and implement k-means and hierarchical clustering.
-   I can identify moments of randomness or user choice in the starting conditions.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "AI-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can write a loop that updates values until perfect convergence is reached.
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/94edce81ecff974c15b15a8e25cad8ec9c7ad095
-   I can explain and implement k-means and hierarchical clustering.
    -   
-   I can identify moments of randomness or user choice in the starting conditions.
    -   

------------------------------------------------------------------------

## \[AI-3\] Generative art:

-   I can apply a variety of generative art functions to make a visually pleasing piece.
-   I can explain why particular changes to the code result in particular differences in the visualization.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 3

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "AI-3", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I can apply a variety of generative art functions to make a visually pleasing piece.
    -   https://github.com/BLauf/BLauf-GitHub_Justification-Fork/commit/ed99846086dbfb8b563e46ec58a64bd8629764b7
-   I can explain why particular changes to the code result in particular differences in the visualization.
    -   

------------------------------------------------------------------------

## \[AI-4\] Creating an algorithm:

-   I can invent and implement my own iterative algorithm.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 1

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "AI-4", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

------------------------------------------------------------------------

# Code Design (CD):

*These objectives relate to making wise or clever choices in how you implement a procedure in code; including creating functions and objects, or thinking about the clarity and efficiency of processes.*

------------------------------------------------------------------------

## \[CD-1\] Speed and Efficiency:

-   I can recognize moments of possible slowdown in my code, and use built-in functions or parallelizing to speed them up.
-   I always use and design vectorized functions whenever possible.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "CD-1", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

------------------------------------------------------------------------

## \[CD-2\] Object handling:

-   I can make reasonable choices in my code design about when to save intermediate objects.
-   I can convert objects between types and structures as needed.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "CD-2", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

------------------------------------------------------------------------

## \[CD-3\] Supporting functions:

-   I write helper/shortcut functions to streamline repeated tasks and make my code easier to read.
-   I use intermediate functions to streamline repeated or looping processes.

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 5

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "CD-3", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   I write helper/shortcut functions to streamline repeated tasks and make my code easier to read.
    -   https://github.com/shreyaaar/VectorVerse/commit/36eaf95d5cddc9cd8513daf01720dc1e2e03cc69
-   I use intermediate functions to streamline repeated or looping processes.
    -   https://github.com/BLauf/STAT431-project-2-master/commit/875f895cd369c7de4e3a56cd203a0fd03d4f66af

------------------------------------------------------------------------

## \[CD-4\] Algorithmic process:

-   My loops are clean and efficient
-   Proper values are calculated to update objects and/or determine stopping conditions
-   I have built in checks for possible problems or extreme cases in the algorithm

```{r, include = FALSE}
## Fill in the line below with your self-assigned level for this objective.
my_level <- 2

portfolio_levels <- portfolio_levels %>%
  bind_rows(c(Objective = "CD-4", 
              Level = my_level))
```

### Level: `r my_level`

### Justification

-   My loops are clean and efficient
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/94edce81ecff974c15b15a8e25cad8ec9c7ad095
-   Proper values are calculated to update objects and/or determine stopping conditions
    -   https://github.com/Cal-Poly-Advanced-R/lab-5-regression-nberzinsCP/commit/94edce81ecff974c15b15a8e25cad8ec9c7ad095
-   I have built in checks for possible problems or extreme cases in the algorithm

------------------------------------------------------------------------

# Summary

```{r, echo = FALSE}
portfolio_levels %>%
  mutate(
    Category = str_extract(Objective, "[A-Z]{2}"),
    Level = factor(Level)
  ) %>%
  ggplot(aes(x = Level, y = (..count..)/sum(..count..))) +
  geom_bar() +
  labs(x = "Level",
       y = "Percent") +
  theme_minimal() +
  scale_y_continuous(labels=scales::percent)
```
